Evaluating the Effects of Tracker Reliability and Field of View on a Target Following Task in Augmented Reality

### 2009-06-25 trunk/Paper/paper.tex
more p values

We examine the effects of level of immersion and tracking sensor reliability in augmented reality (AR) X-ray vision with a virtual reality (VR) based simulation.  We analyze participant performance on a target following task while varying the field of view of the AR display, as well as the reliability of the head tracking sensor.  In low reliability conditions, we simulate sensor dropouts by disabling the augmented view of the scene for brief time periods.  Our study gives insight into the effect of tracking sensor reliability on user performance in a target following task, as well as the relationship between sensor reliability and field of view in an AR system.

@@

We performed two-way {ANOVA} for the time following target metric as an overall analysis of the effects of our two factors.  Figure \ref{fig:anova} gives the results of this analysis.  Both the failure length and the field of view have a very significant effect on performance using this metric.  
% TODO: interaction?

We also used a two-way {ANOVA} to examine the number of times the participant loses the target, with results shown in Figure \ref{fig:anova}.  Both field of view and dropout length have a significant effect.  There also is an interaction between the two factors.  Figure \ref{fig:interaction} shows a plot of this interaction.  
% TODO: need F values reported here.

>>>>

We examine the effect of varying levels of immersion on the performance of a target following task in augmented reality (AR) X-ray vision.  We do this using virtual reality (VR) based simulation.  We analyze participant performance while varying the field of view of the AR display, as well as the reliability of the head tracking sensor as our components of immersion.  In low reliability conditions, we simulate sensor dropouts by disabling the augmented view of the scene for brief time periods.  Our study gives insight into the effect of tracking sensor reliability, as well as the relationship between sensor reliability and field of view on user performance in a target following task in a simulated AR system.

@@

We performed two-way {ANOVA} for the time following target metric as an overall analysis of the effects of our two factors.  Figure \ref{fig:anova} gives the results of this analysis.  Both the failure length and the field of view have a significant effect on performance with this metric, at the $p=0.001$ level.
% TODO: interaction?

We also used a two-way {ANOVA} to examine the number of times the participant loses the target, with results shown in Figure \ref{fig:anova}.  Both field of view and dropout length have a significant effect at the $p=0.001$ level.  There also is an interaction between the two factors at the $p=0.05$ level.  Figure \ref{fig:interaction} shows a plot of this interaction.  
% TODO: need F values reported here.
